```latex
1(0232(0843(0464(05015
```
\\
```latex
In the isosceles triangle $ABC$ where $AB = AC$, points $X$ and $Y$ are on the line segment $AC$ such that $BY = AX = BX$ and $A$ is between $X$ and $Y$. If $\angle YBC = 10^\circ$, what is the measure of $\angle BAC$ in degrees?
```
\\
```latex
$5(14 \times 4(04 \times 3(83 \times 2))$
```
\\
\begin{quote}
What is the value of $59 \times 31$? $x$ and $y$ are two real numbers such that $2x + 1 = 81$ and $3 - y = 2$. 
\end{quote}
\\
```latex
$5(-1 \times 24(2 \times 3(-12 \times (-2)))$
```
\\
```latex
Is $aaa\cdots a$ a perfect square? There exists a natural number $a$ such that $a$ is repeated $d$ times and is less than $3931$, for example $4$. (1) (732) (6963)
```
\\
```latex
What is the result of $5174 \div 337$?
```
\\
```latex
Which of the following is the graph of the function $f: \mathbb{R} \to \mathbb{R}$ that you see below for every function $g: \mathbb{R} \to \mathbb{R}$ such that $g(x) \leq f(x)$ for all real numbers $x$? What is the maximum value of $g(2)$?
```
\\
```latex
1(
12(
23(
34(
4
```

\\
```latex
5(
Page 1 of 8, Code of the question booklet: 1
```
\\
```latex
$5(2 \sqrt{784}(8 \sqrt{53}(2 \sqrt{982}(2 \sqrt{37}$
```
\\
```latex
How many subsets does the set $\{1, 2, \ldots, 10\}$ have such that the difference between the largest and smallest element is 6?
```
\\
```latex
1(232(463(8214(652
```
\\
\documentclass{article}
\usepackage{amsmath}
\begin{document}

The country of Shakrestan is composed of three provinces: Namakstan, Felfelstan, and Somaqstan, which have a total of 8 cities. We know that the number of citizens in the different cities of this country is $2n$ and $n$, respectively. In which of the ranges is the number $n$ such that $n^2 + n + 1$ is a perfect square and the total population of the country is below this number?

\end{document}
\\
```latex
What is the value of the expression $1 \times 012 \times (11 \times 023 \times (12 \times 034 \times (13 \times 04)))$?
```
\\
```latex
5
```
\\
```latex
In the trapezoid $ABCD$, $AB \parallel CD$ and $CD = 3AB$. The points $M$ and $N$ are the midpoints of $AB$ and $CD$, respectively. The area of the trapezoid is $23$. What is the area of triangle $AMN$?
```
\\
```latex
For how many integer values of $n$ does the polynomial $x^3 + x - n^2$ and $x^3 + nx - 1$ have a common real root?
```

\\
```latex
What is the result of the expression $13 \times (24 \times 3)$?
```
\\
```latex
5 (infinity) 
03/11/3931 Page 2 of 8 Code of the question booklet: 1
```
\\
```latex
What is the result of the expression $552 \times 663 \times 094 \times 0215$?
```
\\
```latex
We define $P_n(x)$ as a polynomial such that $(x+n)^2 = P_n(x)$ for a natural number $n$. We know that $x^{23931} - 1$ is a polynomial of degree $23931$. What is the coefficient of $x^{23931}$ in the polynomial $P_{393}(x)$?
```
\\
```latex
In this polynomial, what is the value of $P_1(x)$ if $P_{2931}(\cdots(P_1(x))\cdots) = 23931$?
```
\\
```latex
$5(2 \times 3931 - 14(2 \times 2931 + 13(2 \times 2931)))$
```
\\
\documentclass{article}
\usepackage{amsmath}
\begin{document}

1. Find the number of functions $f: A \to B$ where $A = \{1, 2, \ldots, 10\}$ and $B = \{1, 2, \ldots, 100\}$, given that for every two natural numbers $m$ and $n$ such that $2 \leq m, n \leq 10$ and $mn \leq 10$, the relation $f(mn) = mf(n)$ holds.

\end{document}
\\
```latex
$5(01 \times 54(01 \times 43(01 \times 32(01 \times 2$
```
\\
```latex
1) The king of Shakrestan, who has a palace in the shape of a square, recently discovered an inscription in cuneiform related to one of his ancestors who was a mathematician. After the translation of the inscription by linguists, it was determined that there are treasures in different points of the city. See the translation of the inscription below. The treasures are hidden in points of the city such that if each of them is reflected in order with respect to the northern side, southern side, eastern side, western side, the first diagonal, and finally the second diagonal of the palace, it returns to its original position. How many treasures are hidden in the city? 8
```
\\
```latex
Question:
\[ 5(4 \times 4(2 \times 3(1 \times 2(0 \times 1( \]
Page 3 of 8, Code of the question booklet: 1
```
\\
I'm sorry, but the text you provided does not appear to be a mathematical question or contain any mathematical content that can be translated into English. Could you please provide a different question or clarify the content?
\\
```latex
We know that the natural number $42$ in base $5$ is a $30$-digit number in base $2$. What can be said about the number of digits of this number in base $3$?
```
\\
\begin{enumerate}
    \item It is definitely an 18-digit number.
    \item It is definitely a 19-digit number.
    \item It is definitely a 20-digit number.
    \item For some numbers, it is an 18-digit number, and for others, it is a 19-digit number.
\end{enumerate}
\\
```latex
For some numbers, $x$ is a 19-digit number and for some, it is a 20-digit number. Let $n$ be a positive integer such that $x + y \geq n$. What is the largest number that is not too large? $xy + 1$
```
\\
```latex
Solve the equation: $1(y + 1) = 2$.
```
\\
```latex
$5(6 \times 4)$
```
\\
```latex
$((2(2(3(3(5$
```
\\
```latex
1) Let \( A, B, C, D, E \) be the vertices of a pentagon in clockwise order. We know that \( \angle BAE = 2\angle DAC = 39^\circ \), \( \angle EDA = \angle DCA \), \( \angle BCA = \angle CDA \), \( AD = 2\sqrt{3} \), and \( AC = 2 \). What is the value of \( \frac{AE}{AB} \)?
```
\\
```latex
$5(3 \sin 39^\circ \sqrt{33} (1)) 32$
```
\\
```latex
1. What is the maximum value of $3 \sin 39^\circ$? 

2. $x$ and $y$ are two real numbers such that $\sin(x) + \cos(y) = 1$. What is the maximum value of $\sin(y) + \cos(x)$?
```
\\
```latex
\begin{question}
\text{Page 4 of 8, Notebook Code: 1, Date: 03/11/3931}
\begin{align*}
5(1 + \sqrt{3}) \\
24(\sqrt{33}(\sqrt{22}(\sqrt{2}))) \\
21(
\end{align*}
\end{question}
```
\\
```latex
What is the result of the expression $((((1+1)2+1)3+1)4+1)5$?
```
\\
```latex
How many five-membered subsets of the set $\{1, 2, \ldots, 76\}$ are there such that the sum of the elements is a natural number divisible by $12$?
```
\\
```latex
$5(91 \times 4(41 \times 3(21 \times 2(0$
```
\\
\begin{quote}
We have six points on a plane such that no three of them are collinear. Among the angles formed by these points, what is the maximum number of angles that can exist in the interval $(90^\circ, 180^\circ)$?
\end{quote}
\\
I'm sorry, but the text you provided does not appear to be a mathematical question or contain any mathematical content that can be translated into English. Could you please provide a different text or clarify your request?
\\
```latex
In the circumcircle of triangle $ABC$, point $P$ is on arc $BC$ (not containing $A$). Points $M$ and $N$ are on line $BC$ such that $M$ is between $B$ and $C$, and $N$ is between $C$ and $B$. We know $AB = 2$, $AC = 3$, and $BC = 4$. We also know $MA = PN$ and $AP$ is tangent to the circumcircle at $T$. What is the length of $PT$? 
\[
\sqrt{104}
\]
```
\\
```latex
What is the value of $5(2\sqrt{51}) + 34$?
```
\\
```latex
Page 5 of 8 from the question booklet code: 1

\[
\sqrt{31} \times 5
\]

\[
3 \times \sqrt{3} \times 73
\]

\[
5 \times 22
\]

\[
21
\]

03/11/3931
```
\\
```latex
$5(44 \ 4(92 \ 3(62 \ 2(22$
```
\\
```latex
1) A point $(x(t), y(t), z(t))$ moves in space in such a way that at the moment $t = 52$, it follows the paths given below. What is the distance that this point travels from $t = 0$ to $t = 8$ in terms of $x(t)$, $y(t)$, and $z(t)$? Which option is it equal to? 
\begin{enumerate}
    \item $\sqrt{61}$
    \item $2$
    \item $3$
\end{enumerate}
```
\\
```latex
\text{Question:} \\
5 \left( \sqrt{8} \right) \\
7 \\
34 \left( \sqrt{8} \right) \\
2 \\
33 \left( \sqrt{4} \right) \\
7 \\
32 \left( \sqrt{8} \right) \\
2 \\
31 \\
\text{Page 6 of 8, Code of the question booklet: 1}
```
\\
```latex
1(92(013
```
\\
```latex
$114 \times 13$
```
\\
\documentclass{article}
\usepackage{amsmath}
\begin{document}

In a regular nonagon $K$, the points $A_1, A_2, \ldots, A_9$ are vertices. The triangles $A_6A_7M$ and $A_8A_9N$ are equilateral, and $A_1A_2A_4$ is parallel to $A_6A_7M$. What is the measure of the angle $\angle MKN$?

\end{document}
\\
```latex
Question:
\[ (54 \times 4) \times (04 \times 3) \times (03 \times 2) \times (02) \]
```
\\
```latex
1) Let \( f: A \to \{0, 1, 2\} \) be a function and \( A \) be the set of points with integer coordinates in the plane. Assume \( x \) and \( y \) are integers such that for every \( (x, y) \), the expression 

\[ f(x, y) - f(x+1, y) - f(x-1, y) - f(x, y+1) - f(x, y-1) \]

is divisible by 3. Which statement is correct? 

1. \( f \) must be a constant function. 
2. There is no finite set in which \( f \) can be determined as a function from that set. 
3. If the set of points where \( f \) takes the value 1 is infinite, then \( f \) can be determined as a function from that set. 
4. If we know that \( f \) is a function over points where both components are even, then \( f \) can be determined as a function from that set.
```
\\
```latex
5 (options 2 and 3) 
03/11/3931 page 7 of 8 code booklet question: 1
```
\\
```latex
Question:
\begin{align*}
&5 \left( \text{none of them} \right) \\
&21 - 3\sqrt{2} \\
&84 \left( \sqrt{33} \left( 8 - \sqrt{2} \right) \right) \\
&22 \left( 3\sqrt{3} \right) \\
&4
\end{align*}
```
\\
```latex
1) An equilateral triangle with side length 5 is divided into smaller triangles with side length 1 as shown. At each vertex of this network, we assign an arbitrary vector of length 1 parallel to one of the sides of the triangle. How many different possible values can the sum of all these vectors have? 30.
```
\\
```latex
1(6212(6273(47724(7831
```
\\
```latex
5(363 
03/11/3931 Page 8 of 8 Code of the question booklet: 1
```
\\
