```latex
1(
```
\\
```latex
In triangle $ABC$, point $D$ is on side $AC$ and point $E$ is inside the triangle such that $\angle BAC = 60^\circ$ and $\angle DEC = 30^\circ$. Points $B$ and $D$ are chosen such that $B$ is between $C$ and $D$ on this triangle, and $DE = AB = \sqrt{3}$. What is the ratio $\frac{CD}{BC}$?
```
\\
```latex
Question:
\[ 5(2\sqrt{34}(\sqrt{3} \]
\[ 23(\sqrt{3} \]
\[ 32 \]
```
\\
```latex
1. 2
```
\\
```latex
1) Let \( a, b, c, d \) be real numbers that satisfy the equations \( d + a = 5 \), \( b + c = 3 \), \( ab = 2 \), and \( cd = 4 \). How many possible values exist for \( a \)?
```
\\
```latex
$1(0^2)$
```
\\
```latex
What is the value of $13 \times (24 \times 4)$?
```
\\
\begin{quote}
We have three pairs of screws and nuts: small, medium, and large, but we do not know which screw corresponds to which nut. Each time, we can test one screw with one nut. What is the minimum number of tests needed to ensure that we find the matching nut for each screw in every case?
\end{quote}
\\
```latex
What is the result of the expression $12 \times (23 \times (34 \times 45))$?
```
\\
```latex
Page 1 of 7, Code: 1
```
\\
```latex
1) One or seven

2) One or three or seven

3) Zero or three or seven

4) Zero, one or two or seven
```
\\
```latex
A truncated conical vase with a height of 20 cm and diameters of the mouth and base being 15 cm and 10 cm respectively is placed on the ground. A ball with a radius of 7 cm is placed inside this vase. To which option is the height of the highest point of the ball from the ground (in centimeters) closest?
1
```
\\
```latex
$122 \times 323$
```
\\
```latex
Two real numbers $a$ and $b$ satisfy $a^2 + b^2 = 8$. What is the maximum value of $2(a+b) - ab$?
```
\\
```latex
$5(8 \sqrt{2} 83(2 \sqrt{6})$
```
\\
```latex
In a hotel, there are 31 rooms numbered from 1 to 31. Each room has a key, but not every key is unique. All keys that have the difference between the number written on them and the room number divisible by 3 can open the room. In how many ways can the keys be assigned to the rooms so that all rooms can be opened?
$31!$
```
\\
```latex
$5 \times (4!)$
```
\\
```latex
\[
\frac{(5!)^2}{3! \cdot 4} \left( 5! \times \frac{(4!)^2}{3! \cdot 3} \left( 4! \times \frac{(5!)^2}{22} \right) \right)
\]
```
\\
\begin{quote}
To which option is the value of $\sin(9^\circ)$ closer? $11001 \times (5!) \times (4!)^{21}$
\end{quote}
\\
```latex
Question: 

$5(1 \times 0.53(0.4) - 0.52(-11))$
```

\\
```latex
What is the result of $5931$?
```
\\
```latex
$5 \times (\sqrt{9872} \times \sqrt{59312} \times \sqrt{4931})$
```
\\
```latex
1) In how many ways can 3 matchsticks be removed from the 9 matchsticks present in the figure such that no triangle remains in the figure?
```
\\
```latex
1(62(93(814(72
```
\\
\[
\text{5(08 11. Consider a rectangle with sides 03 and 04, divided into a grid of unit squares by lines parallel to the sides. Take one of the diagonals of the original rectangle. How many of the unit squares in the grid are tangent to this diagonal?}
\]
\\
```latex
1(012(023(034(83
```
\\
```latex
A frog is sitting on the zero point of the integer axis and can jump either to the right or to the left in each step. The length of the jumps of a frog can be any of the numbers $1, 2, \ldots, 4931$. If this frog cannot make two jumps of equal length, how far can it go?
```
\\
```latex
1(362(463
```
\\
```latex
What is the result of $184 \times 121$?
```
\\
```latex
How many ordered quadruples of real numbers $(a, b, c, d)$ satisfy the system of equations below?

\[
\begin{cases} 
a^3 + bc = d^3 \\
b^3 + cd = a^3 \\
c^3 + da = b^3 \\
d^3 + ab = c^3 
\end{cases}
\]
```
\\
```latex
What is the number 12?
```
\\
```latex
Question: 
$$53(52)$$ 
$$4(945(\infty 41)$$ 
Page 3 of 7, Code: 1, Date: 92/11/4931
```
\\
\begin{enumerate}
    \item A cone has only one special point.
    \item Any line that intersects the circular face of the cone must include a special point of the cone.
    \item Any plane that intersects the cone must include a special point of the cone.
    \item All points on the lateral surface of the cone are special.
\end{enumerate}
\\
```latex
There exists exactly one sphere in space such that all the special points of the cone lie on its surface. Ali has discovered a formula for quadratic polynomials that allows him to find the value of a quadratic polynomial at the point $3$ based on its values at the points $0$, $1$, and $2$ as follows: $P(3) = aP(0) + bP$.
```
\\
\begin{quote}
$a$, $b$, and $c$ are three constant numbers. Find these three numbers and determine what $a$, $b$, and $c$ are such that the value of $a - b + c$ is $1$.
\end{quote}
\\
```latex
$54 \times 6$
```
\\
```latex
In how many ways can 8 squares be chosen in the given 5x7 grid such that no two of them are in the same row or column?
```
\\
```latex
Question:
\begin{align*}
512(023(824(235(46 \times 71.
\end{align*}
Page 4 of 7, Code of the question booklet: 1
Date: 92/11/4931
```
\\
```latex
1(992(3013(7014
```
\\
```latex
What is the result of the expression \(111\)?
```
\\
\begin{quote}
Which option represents the set of points $(x, y)$ on the plane with the property that the maximum value among the three expressions $x - y - 1$, $x + y$, and $y^2 - x - y$ is equal to $91$?
\end{quote}
\\
```latex
1)
```
\\
```latex
At the beginning of the first day, a single virus enters the body. At the end of each day, each virus produces 2 new viruses and itself continues to live for $k$ days, where $k$ is the number of days it has lived. How many viruses will be produced at the end of the sixth day?
```
\\
```latex
1(982(2113(8214(441
```
\\
```latex
In how many ways can the number $12$ be written as the sum of consecutive natural numbers, where the order of the numbers does not matter?
```
\\
```latex
1(0 2(953 9114(971
```
\\
```latex
Question: 
Page 5 of 7, Code 4931/11/92, 932(5)
```

\\
```latex
What is the result of the expression $512(613(714(81)))$?
```
\\
```latex
We want to install cylindrical columns at all points of a regular grid, except for the central point of a $5 \times 5$ grid, in such a way that the central point is not visible from the outside. This means that in the flat map you see, every line passing through the central point intersects at least one of the circles. If the distance between adjacent points is $1$ meter, what is the minimum required radius of the column cross-section in meters? $\sqrt{2}$
```
\\
```latex
5(\sqrt{4} \cdot 714(\sqrt{1} \cdot 53(\sqrt{1} \cdot 012(\sqrt{1} \cdot 31
```

\\
```latex
1(32. We say that a plane can be tiled with a polygon if it is possible to place infinitely many copies of that polygon on the plane in such a way that they cover the entire plane and, except possibly at the edges, do not overlap. With which shapes is it not possible to tile the plane?
```
\\
```latex
$0^2$
```
\\
```latex
Question: 

$13 \times 2$

$4 \times 3$
```
\\
```latex
We have the numbers $5\sqrt{3}$, $5\sqrt{5}$, and $7\sqrt{3}$, which we denote as $A$, $B$, and $C$, respectively. Which option is correct?

1. $A < B < C$

2. $A < C < B$

3. $B < C < A$

4. $C < B < A$

5. $A < B < C$

We have a sequence $a_1, a_2, \ldots, a_{51}$ from the set $\{1, 2, 3, \ldots, 30\}$ such that for every $1 \leq i, j \leq 51$ with $i + j \leq 51$, we have $a_{i+j} > a_i + a_j$. What is the value of $a_{62}$?
```
\\
```latex
$0^2$
```
\\
```latex
What is the result of the expression $13 \times (44 \times 95)$?
```
\\
```latex
Page 6 of 7, Code: 1
```
\\
```latex
$0^2$
```
\\
```latex
What is the number $13$?
```
\\
```latex
What is the value of \( 54 \times 6 \)?
```
\\
```latex
Consider the sequences $\{x_n\}$ and $\{y_n\}$ of real numbers for $n \geq 0$ that satisfy the following recurrence relations:
$$ x_{n+1} = x_n^2 + x_n y_n + y_n^2, $$
$$ y_{n+1} = x_n^2 - x_n y_n + y_n^2. $$

If $x_0$ and $y_0$ are positive numbers such that $x_0 + y_0 = 2$, and $S = x_8 + y_8$, which of the following is correct?
\begin{itemize}
    \item $S < 205$
    \item $205 \leq S < 2002$
    \item $2002 \leq S < 2008$
    \item $2008 \leq S < 20024$
    \item $20024 \leq S$
\end{itemize}
```
\\
\begin{enumerate}
    \item Let $B$ and $D$ be given points on the line $BC$ of triangle $ABC$ with $\angle BAC = 40^\circ$. Point $D$ is located on line $BC$ such that it intersects $AB$ and $AC$ at points $E$ and $F$, respectively. Similarly, draw perpendiculars from $E$ and $F$ to $AB$ and $AC$, respectively, such that they intersect $BC$ at points $K$ and $L$. We know that $K$ is the foot of the perpendicular from $E$ to $AB$ and $L$ is the foot of the perpendicular from $F$ to $AC$. If $K$ is on line $AB$ and coincides with point $B$, what is the measure of $\angle ACK$ in degrees?
\end{enumerate}
\\
```latex
$2(04)3(06)4(08)5(001)$
```
\\
```latex
1) Consider a formula with three variables $x, y, z$ where the variables are from the set $\{0, 3\}$. The functions minimum and maximum are used, such as in the following three formulas: $\min(\max(x, z), y)$; $\min(x, x)$; $\max(x, \min(x, y))$. We say two formulas are different if there exists a value for the variables $x, y, z$ such that the two formulas compute different values for them. For example, the two formulas $\max(x, \min(x, y))$ and $\min(x, x)$ are not different. How many different formulas do we have?
```
\\
```latex
Evaluate the expression \( 112 \times (813 \times (464 \times 652)) \).
```
\\
```latex
Question:
\begin{quote}
5 (infinity) \\
Page 7 of 7 \\
Code of the question booklet: 1
\end{quote}
```
\\
